% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2017 Alison Chan <alisonc@alisonc.net> http://alisonc.net/
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
% Roboto and Inconsolata fonts
\usepackage[sfdefault]{roboto}
\usepackage{zi4}
\robustify\cftdotfill

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
\newlength{\listsep}
\setlength{\listsep}{-0.1\baselineskip}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{4pt}
  \parbox{\textwidth}{
      \framebox[\textwidth][l]{
          {\textbf{\sffamily{\large #1}}}
      }
  }
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{\textwidth}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------
\begin{document}
\ifdef{\MONSTER}{\def\PUBLIC{}}{}
\ifdef{\DICE}{\def\PUBLIC{}}{}

\begin{tabular}{b{4cm} c b{12cm}}
	\textbf{\huge Alison~Chan} & \hspace{6pt} & \parbox[b]{12cm}{\textbf{Detroit~MI} \\
		\ifdef{\PUBLIC}{\ifdef{\MONSTER}{\href{mailto:resm@alisonc.net}{\nolinkurl{resm@alisonc.net}}%
			}{\ifdef{\DICE}{\href{mailto:resd@alisonc.net}{\nolinkurl{resd@alisonc.net}}%
				}{\href{mailto:res@alisonc.net}{\nolinkurl{res@alisonc.net}}%
		}}}{\href{mailto:hireme@alisonc.net}{\nolinkurl{hireme@alisonc.net}}}~\textbullet~%
		\ifdef{\PUBLIC}{Email~for~phone~number}{\href{tel:+19092787753}{+1~909~278~7753}}~\textbullet~%
		\href{https://alisonc.net/}{\nolinkurl{alisonc.net}}~\textbullet~%
		\href{https://github.com/alis0nc}{\nolinkurl{github.com/alis0nc}}}
\end{tabular}
\vspace{4pt}

{\large
Generalist software engineer with a track record of producing clean code, eliminating technical debt,
and digging into complicated problems spanning multiple systems. 
% Modify this sentence if needed. 
Seeking a challenging software engineer position with opportunities to learn new technologies and advance to senior technical roles.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Professional Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ressubheading{Fund for Equal Justice}{Detroit MI}{Assistant}{January 2018 -- present}
\begin{itemize}\itemsep \listsep \small
	\resitem{Implemented a mail merge document to produce donation acknowledgement letters.}
	\resitem{Entered historical donation records from copies of cancelled checks into a spreadsheet.}
\end{itemize}

\ressubheading{GrubHub}{Oakland County MI}{Driver Partner {\small (independent contractor)}}{November 2017 -- present}
\begin{itemize}\itemsep \listsep  \small
	\resitem{Retrieved food orders from restaurants and delivered them to customers in a timely and efficient manner.}
	\resitem{Communicated with customers and restaurants to assess pickup and delivery needs and provide information of order status.}
	\resitem{Maintained accurate records of mileage driven in each shift.}
\end{itemize}

\ressubheading{X by 2}{Farmington Hills MI}{Software Engineering Consultant}{October 2015 -- August 2017}
\begin{itemize}\itemsep \listsep  \small
    \resitem{{\bf Client project: Claims System for Auto-Owners Insurance}}
    \resitem{Reengineered document management integration middleware based on Java EE/Apache Camel/Spring, focusing on cleaner data model, cleaner APIs,
    	     and better fault tolerance. This led to fewer system errors, improved performance, and easier troubleshooting.}
    \resitem{Customised COTS application front end with vanilla JavaScript and Gosu code, resulting in improved workflow for end users as well as better performance.}
    \resitem{Led design review, code review, and data model discussions.}
    \resitem{Troubleshooted integration errors, working closely with external vendors and other departments in the client 
    	     organisation. Performed data fixes and code hotfixes in the production environment.}
    \resitem{{\bf Internal consulting project: Applicant Tracking / HR System}}
    \resitem{Collaborated with X by 2 principals to gather requirements for a cloud based applicant tracking
             and HR administration system to replace various home-grown applications.}
    \resitem{Researched and contacted potential vendors for requirements analysis and demos with stakeholders.}
\end{itemize}

\ifdef{\SHALEM}{
\ressubheading{Kettering University}{Flint MI}{Department of Computer Science : Research Assistant}{April 2013 -- June 2015}
\begin{itemize}\itemsep \listsep \small
    \resitem{Configured OpenFlow software defined networking switches for Kettering's 
    	     Laboratory for Advanced Network Applications and developed and tested OpenFlow controller applications.}
\end{itemize}


\ressubheading{Kettering University}{Flint MI}{Department of Customer Service \& Programs : Student Caller}{July 2012 -- September 2015}
\begin{itemize}\itemsep \listsep \small
    \resitem{Invited prospective students to Kettering open house events and followed up with postcards 
             and phone calls after those events.}
\end{itemize}

\ressubheading{Livio}{Ferndale MI}{Software Engineering Co-op}{September 2012 -- December 2012}
\begin{itemize}\itemsep \listsep \small
    \resitem{Developed iOS apps and backend network code for sales demonstrations.}
\end{itemize}
}{}

\ressubheading{New Eagle}{Ann Arbor MI}{Software Engineering Co-op}{October 2010 -- June 2012}
\begin{itemize}\itemsep \listsep \small
    \resitem{Created HMI applications for embedded display hardware and PC applications to calibrate electronic control modules.}
    \resitem{Worked with product managers to evaluate products being considered for distribution.}
\end{itemize}
%\def\OMITVOLUNTEER{}

\resheading{Volunteer Experience}

\ressubheading{Kibbutz Detropia}{Detroit MI}{Tech Maven}{September 2017 -- present}
\begin{itemize} \itemsep \listsep \small
	\resitem{Overhauled Kibbutz Detropia's online presence, including revamping the website (\url{http://kibbutzdetropia.org}), administering a Google Apps for Nonprofits instance, and updating social media profiles.}
	\resitem{Tended vegetable gardens and cleaned up litter and illegal dump sites in the neighborhood.}
	\resitem{Cooked for weekly vegan/vegetarian public Shabbat dinners.}
\end{itemize}

\ressubheading{Penguicon}{Southfield MI}{Assistant Head of Logistics $\rightarrow$ Head of Logistics}{December 2015 -- present}
\begin{itemize} \itemsep \listsep \small
	\resitem{Oversaw the annual process of inventorying the property of a 1600-attendee open source/science fiction/DIY convention.}
	\resitem{Coordinated the transportation of convention property between the storage location and the convention venue, including scheduling load-in and load-out times, determining volunteer staff needs, and directing volunteers during load-in and load-out.}
\end{itemize}

\ifdef{\SHALEM}{\def\PROJECTS{}}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Projects}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.5\baselineskip}
\begin{itemize} \itemsep 2\listsep
	\item {\bf Bendyboi Tracker} (\url{https://github.com/alis0nc/bendyboi-tracker}): A Discord bot that serves as a front end to the bus tracker API of a local public transit system. It provides a query interface to the bus tracker through Discord messages, and sends alerts when certain buses begin or end their runs.
    \item {\bf DDOT Bus Mapping} (in progress): Surveying Detroit Department of Transportation bus routes and entering stop locations in OpenStreetMap.
    \item {\bf psoaas} (\url{https://github.com/alis0nc/psoaas}): A web service wrapper for the PDF file size optimiser \texttt{pdfsizeopt}, built with Node.js and Express.
    
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.5\baselineskip}
\begin{itemize} \itemsep 2\listsep
    
    \item {\bf Programming languages:} Python; Java; Gosu; JavaScript; shell script; C$\sharp$
    \item {\bf Frameworks:} Apache Camel; Spring Web Services; Spring Boot; Express
    \item {\bf Databases:} MS SQL Server
    \item {\bf Operating systems:} Linux (desktop \& embedded); Windows
    \item {\bf Networking:} Ubiquiti EdgeOS and UniFi platform; TCP/IP; IPv6 dual-stack environments
    \item {\bf Workflow:} git; GitHub; JIRA; Travis-CI; Jenkins; bash script
    
\end{itemize}
%\ifdef{\SHALEM}{\eject}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ressubheading{Kettering University}{Flint MI}{Coursework completed for dual degree BS Computer Science / BS Computer Engineering}{2010 -- 2015}
\begin{itemize}\itemsep \listsep \small
   \resitem{Systems and Data Security concentration}
   \resitem{International Studies minor}
\end{itemize}


\end{document}
